\documentclass{letter}
\usepackage{hyperref}
\signature{Jordan Bell}
\address{619 Woodbine Ave., Apt. 103 \\ Toronto, ON, M4E 2J2  \\ 416 528 3258  \\  \url{jordan.bell@gmail.com}\\ \url{https://www.linkedin.com/in/jordanbell2357/}}
\begin{document}

\begin{letter}{Operation Smile Canada (OSC) \\ 375 University Ave., Suite 204 \\ Toronto, ON, M5G 2J5}
\opening{Dear Recruitment Team,}

I am writing to express my keen interest in the Director, Database Management, Finance \& Analytics role at Operation Smile Canada. With a comprehensive background in business intelligence and data management, I am excited about the opportunity to contribute to your accomplished and respected organization, which resonates deeply with my professional skills and personal values of impact, compassion, resilience, and integrity.

In my recent role as a Business Intelligence Developer at Donor Compass, I have honed my expertise in managing CRM activities and ensuring data integrity, which aligns perfectly with the responsibilities of this role at Operation Smile Canada. My experience with Blackbaud and PowerBI, coupled with my proficiency in SQL and Python, has equipped me to lead initiatives in data analysis, fundraising analytics, and CRM system management. I am particularly drawn to this role's emphasis on cross-departmental collaboration and data integration, areas where I have successfully demonstrated my capabilities in past positions.

Your requirement for a leader who can oversee and optimize system processes across various teams resonates with my experience in operational efficiency and client-centric achievements. At Canadian Tire, I led projects focusing on data pipeline development and business intelligence, where I developed metrics and PowerBI dashboards to drive strategic decision-making. My role also involved ensuring compliance with fiscal, legal, and regulatory requirements, which I understand is a critical aspect of the Director's role at Operation Smile Canada.

Furthermore, I am passionate about fostering a culture of data proficiency and ongoing learning within teams. My tenure as a Mathematics Course Instructor and Tutor at the University of Toronto and in my private practice has equipped me with the skills to provide effective training, guidance, and mentorship. This experience, combined with my leadership roles in data management and analytics, positions me well to lead the Database team at Operation Smile Canada, ensuring the highest standards of reporting, gift entry responsibilities, and PCI compliance regulations.

I am enthusiastic about the possibility of bringing my blend of technical expertise and passion for data-driven decision-making to Operation Smile Canada. I look forward to potentially discussing how my background, skills, and enthusiasms align with the needs and vision of your organization.

Thank you for considering my application. I am eager to further discuss how I can contribute to the success of OSC.

\closing{Warm regards,}

\end{letter}
\end{document}