\documentclass{letter}
\usepackage{hyperref}
\signature{Jordan Bell}
\address{619 Woodbine Ave., Apt. 103 \\ Toronto, ON, M4E 2J2  \\ 416 528 3258  \\  \url{jordan.bell@gmail.com}\\ \url{https://www.linkedin.com/in/jordanbell2357/}}
\begin{document}

\begin{letter}{Operation Smile Canada (OSC) \\ 375 University Ave., Suite 204 \\ Toronto, ON, M5G 2J5}
\opening{Dear Recruitment Team,}


[Your Name]
[Your Address]
[City, State, Zip]
[Email]
[Phone Number]
[Date]

[Recipient's Name]
[Recipient's Title]
[Company Name]
[Company Address]
[City, State, Zip]

Dear [Recipient's Name],

I am writing to express my strong interest in the [Position Name] role at [Company Name]. With a robust background in data engineering and a profound passion for creating comprehensive data universes, I believe I am well-suited to contribute significantly to your team. My expertise in Python, SQL, and various ETL tools, coupled with my specialization in geospatial data analysis and satellite earth observation, allows me to handle complex datasets with precision and insight. My experience extends to IoT data, particularly AIS messages for vessel positions, where I have innovated in feature engineering to infer port visits by analyzing the duration of vessel proximity to ports.

My journey in data science began in adolescence when I created a website featuring a complete list of mods for first-person shooter games. This initial foray into assembling self-contained data universes has evolved with my professional skills, leading to more complex and impactful projects. My recent endeavors include a comprehensive project on AIS data, where I developed methodologies to validate vessel port visits against official port authority records. This project, while currently on hold, exemplifies my passion for and capability in managing extensive data projects with real-world applications.

Currently, I am channeling my expertise into a new venture focused on the real estate boom in Ontario. This project involves assembling and harmonizing diverse geospatial datasets, including night-time light raster data from NASA, infrastructure data from OpenStreetMap, native land claims, and real estate data, among others. This initiative is not only a testament to my technical abilities but also to my commitment to creating data-driven solutions that have tangible impacts on industries and communities.

My experience also includes a comprehensive analysis of the gold production industry, where I independently aggregated and harmonized data from various public sources, demonstrating my ability to delve deeply into specific sectors. This project, along with my proficiency in granular HS Codes and unit measurements, underscores my meticulous attention to detail and my capability to manage data with precision and accuracy. I am excited about the possibility of bringing my unique blend of skills and passion to [Company Name], contributing to your team's success and furthering your data-driven initiatives.

Thank you for considering my application. I look forward to the opportunity to discuss how my skills and experiences align with the goals of [Company Name] and how I can contribute to your team.
\closing{Warm regards,}

\end{letter}
\end{document}