\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking} % style options are 'casual' (default), 'classic', 'oldstyle', and 'banking'
\moderncvcolor{blue} % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage[scale=0.87]{geometry} % adjust the page margins
\usepackage{microtype} % Better typography
\usepackage{fontawesome5}



% Personal data
\name{Jordan}{Bell}
\phone[mobile]{416-528-3258}
\email{jordan.bell@gmail.com}
\social[linkedin]{jordanbell2357}
\social[github]{jordanbell2357}
\social[kaggle]{jordanbell2357}
\homepage{jordanbell.info}
\extrainfo{\href{https://www.credly.com/users/jordanbell2357/badges}{Credly Profile}}

\begin{document}
\makecvtitle

\section{Business Intelligence Developer}
Experienced Business Intelligence Developer with a Master of Science in Mathematics, specializing in
data pipeline development and geospatial and time series data analysis. Exceptional at bringing order to disorganized data assets,
producing top-quality business intelligence dashboards, creating/evaluating/deploying machine learning models, and with technical
communication and documentation.

\section{Key Skills}

\cvitem{Data Cleaning and Engineering}{Proficient in data cleaning and engineering, ensuring data quality and integrity.}
\cvitem{SQL Pipeline Development}{Experienced in developing efficient SQL data pipelines for complex data processing.}
\cvitem{Database Administration}{Expertise in database design, administration, data documentation, and stewardship.}
\cvitem{ETL Processes}{Adept at designing and executing ETL processes for data transformation and integration.}
\cvitem{Business Intelligence Dashboards}{Skilled in creating insightful business intelligence dashboards for data-driven decision-making.}
\cvitem{Machine Learning}{Proficient in applying machine learning techniques for predictive modeling and data analysis.}
\cvitem{Time Series Analysis}{Specialized in classical time series analysis, including ARIMA and related methods.}
\cvitem{Geospatial Analysis}{Expert in conducting comprehensive geospatial data analyses.}
\cvitem{Linux Systems Administration}{Competent in Linux systems administration, managing and optimizing system performance.}
\cvitem{Computer Networking}{Knowledgeable in computer networking, ensuring robust and secure network infrastructures.}
\cvitem{IT Support}{Experienced in providing effective IT support and troubleshooting.}
\cvitem{Technical Training}{Skilled in developing and delivering technical training programs, enhancing team capabilities.}



% Professional Experience
\section{Professional Experience}
\cventry{November 2023--February 2024}{Business Intelligence Developer}{Donor Compass}{Toronto, Ontario, Canada (Remote)}{}{
\begin{itemize}%
\item Facilitated secure data transfers with clients, focusing on optimizing data fields and filters for enhanced processing efficiency.
\item Pioneered the transformation of raw data into actionable insights using advanced data manipulation and engineering techniques.
\item Innovated and maintained PowerBI dashboards, integrating client data with scoring algorithms to illustrate donor propensity.
\item Led the modernization of data sharing infrastructure from traditional VPN and Samba sharing to Citrix ShareFile, significantly improving security and accessibility.
\item Transitioned the legacy scoring engine to a virtual machine environment, managing configurations for PHP, Redis, MySQL, and Liquibase.
\item Overhauled client data management systems, establishing systematic databases and assuming the role of database administrator.
\item Employed Python and pandas for efficient data cleaning, complementing and enhancing SQL-based data processes.
\item Utilized PostgreSQL for robust database management, handling large-scale datasets with a focus on accuracy and speed.
\item Proactively addressed and resolved VPN and network-related issues, ensuring smooth and uninterrupted operations.
\item Left a strong impact in a short tenure before the company's insolvency; received commendation from manager, available for reference.
\end{itemize}}


\cventry{June 2022--August 2023}{Data Science Associate}{Canadian Tire}{Toronto}{}{
\begin{itemize}%
\item Developed store similarity metrics comparing store sales at any level of aggregation of product.
\item Participated in planning and creating pipeline for Google Analytics page view data into OLAP database, for store similarity calculations
\item Orchestrated the integration of geospatial census data and Environics data, linking regional characteristics to surrounding Canadian Tire stores by postal code to inform strategic business decisions.
\item Developed a robust and dynamic OLAP database table view to produce a dashboard for monitoring dealer participation in promotional deals. This involved complex windowing functions and time span standardization using step functions for variable deal lengths, facilitating real-time and historical analysis.
\end{itemize}}

\cventry{January 2019--April 2019}{Data Science Intern}{Consilium Crypto}{Toronto}{}{
\begin{itemize}%
\item Engineered a novel approach to feature engineering for time series data, integrating price and volume data from multiple cryptocurrency exchanges with blockchain transaction data to enhance predictive model robustness.
\item Designed and tested a logistic regression model to analyze Ethereum data, identifying key indicators that influence price and volume movements.
\item Utilized domain knowledge to select significant time periods revered by the trading community, which informed the feature engineering process and enriched the model's predictive power.
\end{itemize}}

\cventry{January 2021--June 2022}{Mathematics Tutor}{Jordan Bell Tutoring}{Toronto}{}{}

\cventry{March 2018--January 2021}{Mathematics Tutor}{Toronto Elite Tutorial Services}{Toronto}{}{}

\cventry{April 2013--April 2017}{Mathematics Course Instructor}{University of Toronto}{Toronto}{}{
\begin{itemize}%
\item Mentored students and developed course materials.
\item Organized teaching assistant duties, time allocation, and preparation of materials for use in tutorials.
\item Instructor for multivariable calculus, ordinary differential equations, and linear algebra courses, as single instructor and as part of multiple section courses (first and second year courses with versions for different programs).
\end{itemize}}

\cventry{September 2009 - April 2013}{Mathematics Teaching Assistant}{University of Toronto}{Toronto}{}{
\begin{itemize}%
\item 1st year courses: Calculus for engineers, computer science, biology, and math specialists (separate courses), and linear algebra for engineers and computer science. 2nd year courses: Mathematical writing (essay marking), linear programming, ordinary differential equations for computer science and for math specialists (separate courses). 3rd year courses: Complex analysis, functional analysis, group theory, partial differential equations, dynamical systems. 4th year courses: Nonlinear optimization
\end{itemize}}

% Education
\section{Education}
\cventry{2018--2019}{Graduate Certificate}{Analytics for Business Decision Making (SAS based program)}{George Brown College}{Toronto}{}
\cventry{2009--2017}{Ph.D. candidate in mathematics: Candidacy Achieved 2011, Withdrawn 2016}{Department of Mathematics}{University of Toronto}{Toronto}{Canada Graduate Scholarships, Doctoral (CGS D)}
\cventry{2007--2009}{Master of Science}{Department of Mathematics}{University of Toronto}{Toronto}{Canada Graduate Scholarships, Master’s (CGS M)}
\cventry{2003--2007}{Bachelor of Mathematics}{Mathematics}{Carleton University}{Ottawa}{University Medal in Mathematics}

\section{Languages}

\cvitem{SQL}{MySQL, PostgreSQL, Hive, SparkSQL, Google BigQuery, Oracle, Teradata}
\cvitem{NoSQL}{Redis, MongoDB}
\cvitem{Python}{Python programming language}
\cvitem{Scripting}{Bash scripting and CLI tools such as awk, sed, gnuplot, ImageMagick, ffmpeg, GDAL}
\cvitem{Statistical \& Data Analysis}{R, SAS, Excel, PowerBI DAX and Power Query M}
\cvitem{Theoretical}{Automata theory and regular expressions, relational algebra}



\section{Software and Platforms}

\begin{tabular}{p{0.60\textwidth} p{0.30\textwidth}}
    \textbf{Software}                  & \textbf{Platforms}                                    \\
    \hline
    Hitachi Pentaho                    & Amazon S3                                              \\
    Talend                             & Microsoft Azure                                       \\
    Dataiku, KNIME                              & Google Cloud Platform                                  \\
    PowerBI, Tableau, MicroStrategy & Databricks                                             \\
    Excel, Google Sheets               & Hadoop HDFS                                             \\
    ArcGIS, Mapbox, CARTO             & Cloudera                                               \\
    Linux shell scripting              &  Teradata                                                \\
    git, SSH, PGP                     &  Oracle                                         \\
    Docker                            & Redis                                                 \\
    VMware, Virtualbox                & Datadog, Elasticsearch, Splunk                                                \\
    Lucidchart, Oracle SQL Developer  & Google Analytics                                        \\
    Microsoft Teams, SharePoint       & Atlassian Bitbucket, Confluence, Jira                  \\
    Cisco Packet Tracer, Nmap, Wireshark & Citrix ShareFile \\
\end{tabular}
    

\section{Python Libraries Working Experience}

\cvitem{Data Manipulation}{NumPy, pandas, PySpark, Dask, imageio, librosa}
\cvitem{Data Modeling}{Pydantic, erdantic, SQLAlchemy}
\cvitem{Visualization}{Matplotlib, Seaborn, Graphviz}
\cvitem{Regression, Classification, \& Clustering}{sklearn, scipy.spatial}
\cvitem{Deep Learning}{Keras, TensorFlow, PyTorch}
\cvitem{Time Series Analysis}{statsmodels.tsa, sktime, pmdarima, tsfresh, scipy.signal, scipy.fft}
\cvitem{Text Processing}{re, sklearn.preprocessing, sklearn.feature\_extraction, automata-lib, spaCy, NLTK, Gensim}
\cvitem{Geospatial Data}{GeoPandas, Rasterio, xarray, h3, Cartopy}
\cvitem{Bayesian Estimation}{ArviZ, PyMC3}
\cvitem{Numerical Mathematics}{scipy.integrate, scipy.optimize, Theano}
\cvitem{Symbolic Mathematics}{SymPy}

\section{Selected Personal Projects}

\cvitem{\textbf{USCG NAIS Data Project}}{%
\url{https://github.com/jordanbell2357/uscg-nais-data}
\begin{itemize}
    \item Analyzed AIS data to estimate shipping activity.
    \item Created visualizations for maritime traffic data.
    \item Processed 1-minute frequency AIS message data for 2022 for all vessels in US coastal and inland waters (2.9 billion entries).
    \item Conducted feature engineering for sessionizing vessel activity.
\end{itemize}
}

\cvitem{\textbf{Canada 2021 Census by Forward Sortation Areas}}{%
\url{https://github.com/jordanbell2357/canada-2021-census}
\begin{itemize}
    \item Conducted clustering and regression analyses on census data.
\end{itemize}
}



\section{Selected Online Courses}

\cvitem{Teradata}{\href{https://www.credly.com/earner/earned/badge/100a7cd0-8356-4442-b991-0abc20307537}{Intro to Advanced SQL Engine 17.10}}
\cvitem{Datadog}{\href{https://www.credly.com/earner/earned/badge/41003b6f-fdb9-456b-a97d-6b9972147175}{Fundamentals I}}
\cvitem{Talend}{\href{https://www.credly.com/earner/earned/badge/7a0e8e9b-6984-4973-a6a6-3acd028d0532}{Data Fabric Explorer}}
\cvitem{IBM}{\href{https://www.credly.com/earner/earned/badge/4242d25d-435d-4a3e-8114-0b8c059aa7f4}{Containers \& Kubernetes Essentials}}
\cvitem{Cloudera}{\href{https://coursera.org/share/758c31b0eca67317d378432811a49eae}{Modern Big Data Analysis with SQL}}
\cvitem{Microsoft}{\href{https://coursera.org/share/3a9b0b2b40a9cbe9f257ca1000ea0271}{Azure Data Fundamentals DP-900 Exam Prep}}
\cvitem{AWS}{\href{https://coursera.org/share/add6daea4dd38b3d06e02647736c9481}{Fundamentals by Amazon Web Services}}
\cvitem{Google}{\href{https://www.credly.com/badges/edcdba60-5676-4202-91d0-aec1247fe104/linked_in_profile}{Data Analytics Certificate}}
\cvitem{The Linux Foundation}{\href{https://www.credly.com/badges/3ca0eef0-4775-4a38-bae5-c500e12a35cc/linked_in_profile}{Open Source Software Development, Linux and Git Specialization}}


\section{Selected Publications}

\cvitem{}{
Bell, Jordan, and Viktor Blåsjö. “Pietro Mengoli’s 1650 Proof that the Harmonic Series Diverges.” \textit{Mathematics Magazine} 91, no. 5 (2018): 341–47. \url{https://doi.org/10.1080/0025570X.2018.1506656}. 2019 recipient of the \href{https://www.maa.org/programs-and-communities/member-communities/maa-awards/writing-awards/carl-b-allendoerfer-awards}{Carl B. Allendoerfer Award}, MAA.
}

\cvitem{}{
Andrews, George E., and Bell, Jordan. “Euler's Pentagonal Number Theorem and the Rogers-Fine Identity.” \textit{Annals of Combinatorics} 16 (2012): 411–420.\url{https://doi.org/10.1007/s00026-012-0139-4}
}

\cvitem{}{
Bell, Jordan. “A Summary of Euler’s Work on the Pentagonal Number Theorem.” \textit{Archive for History of Exact Sciences} 64, no. 3 (2010): 301–73.\url{https://doi.org/10.1007/s00407-010-0057-y}
}

\cvitem{}{
Bell, Jordan, and Brett Stevens. “A Survey of Known Results and Research Areas for $n$-Queens.” \textit{Discrete Mathematics} 309, no. 1 (2009): 1–31. \url{https://doi.org/10.1016/j.disc.2007.12.043}. Cited by 250+ publications.
}




\end{document}